### 2018-04-14 experiments.tex
fixup

Figure \ref{hashbug} shows TSTL code for generating inputs to the {\tt
  datarray} algorithms.  Running this harness using TSTL's {\tt
  --checkProcessDeterminism} flag requires less than 10 seconds on
average to produce a test exhibiting process-level nondeterminism.

>>>>

Figure \ref{hashbug} shows TSTL code for generating inputs to the {\tt
  datarray} algorithms.  Running this harness using TSTL's {\tt
  --checkProcessDeterminism} flag requires less than 10 seconds on
average to produce a test exhibiting process-level nondeterminism in
the {\tt calc\_marginals\_sumproduct} function (the only broken algorithm).
